Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

In the case of other internal change factors other than IS1, all test results
with three significant values can be successfully detected and the source can be determined because the algorithm can determine that the CDF data latency case regression
has a different distribution with the CDF baseline latency data. While on cases that simulate changes from external, i.e. cases ES1 to
ES4, PRA Engine can also detect the occurrence of regression but the results of critical analysis
path cannot determine the source of the regression because it does not
caused by changes in service level.

>>>>

In the case of other internal change factors other than IS1, all test results
with three significant values can be successfully detected and the source can be determined because the algorithm can determine that the CDF data latency case regression
has a different distribution with the CDF baseline latency data. While on cases that simulate changes from external, i.e. cases ES1 to
ES4, PRA Engine can also detect the occurrence of regression but the results of critical path analysis cannot determine the source of the regression because it does not caused by changes in service level.
